To log or not to log

### 2022-07-15 analysis/Analysis ECDC forecasts.Rmd
update figures, manuscript, add citations

ggsave("output/figures/HUB-mean-obs-location.png", width = 9, height = 8)

@@

```{r}
# plot with mean vs. variance --------------------------------------------------
hub_data |>
  dplyr::select(location, target_type, target_end_date, true_value) |>
  unique() |>
  group_by(location, target_type) |>
  summarise(mean_value = mean(true_value), 
            sd_value = sd(true_value), 
            var_value = var(true_value)) |>
  ggplot(aes(y = var_value, x = mean_value)) +
  geom_point() + 
  facet_wrap(~ target_type, scales = "free") + 
  scale_x_continuous(trans = "log10", labels = label_fn) +
  scale_y_continuous(trans = "log10", labels = label_fn) +
  # scale_x_continuous(labels = label_fn) +
  # scale_y_continuous(labels = label_fn) +
  labs(y = "Variance observed value", x = "Mean observed value") + 
  geom_function(fun = function(x) x^2, linetype = "dashed", size = 0.5) + 
  theme_scoringutils() + 
  geom_smooth(alpha = 0.2, size = 0.2)

ggsave("output/figures/HUB-mean-var-obs.png", width = 7, height = 4)

@@

*Scores are more comparable across targets*

@@

```{r}
scores |> 
  filter(model == "EuroCOVIDhub-ensemble") |>
  group_by(scale, target_type, horizon) |>
  summarise(interval_score = mean(interval_score), 
            .groups = "drop_last") |>
  mutate(multiplicative_score = interval_score / min(interval_score)) |>
  ggplot(aes(y = multiplicative_score, x = horizon)) + 
  geom_line() + 
  geom_point() + 
  facet_grid(target_type ~ scale) + 
  theme_scoringutils() + 
  labs(x = "Forecast horizon in weeks", y = "Multplicative change in interval score")

ggsave("output/figures/HUB-scores-over-horizon.png", width = 7, height = 5)

@@

*Slightly less increase on the log scale, but overall not a lot of difference*

## Actual model rankings for single forecasts

```{r}
# we see that rankings change even for a single forecast. So we need to check everything is still correct. 
# take one example
test_data <- hub_data |>
  filter(model %in% c("MUNI-ARIMA", "epiforecasts-EpiNow2"), 
         forecast_date == "2021-10-18", 
         target_type == "Cases", 
         location == "AT")

test_data |>
  mutate(prediction = log(prediction), 
         true_value = log(true_value)) |>
  score(metrics = c("interval_score")) |>
  summarise_scores()
## indeed everything seems to be correct, but rankings still change FOR A SINGLE FORECAST. 
# It seems this is because the trade-off between calibration and sharpness changes? 
# need to check in what way

rankings <- scores |>
  select(-c(coverage_deviation, bias, aem, sharpness, underprediction, overprediction)) |>
  group_by(location, forecast_date, horizon, target_type, scale) |>
  mutate(ranking = rank(interval_score) / n()) |>
   filter(forecast_date == "2021-10-18", 
         target_type == "Cases", 
         location == "AT")

factor_levels <-  rankings |>
  filter(horizon == 2, scale == "natural") |>
  group_by(model) |>
  summarise(ranking = mean(ranking)) |>
  arrange(-ranking) |>
  pull(model)

p_rankings <- rankings |>
  filter(horizon == 2) |>
  mutate(model = factor(model, levels = factor_levels)) |>
  ggplot(aes(y = model, x = ranking)) +
  ggdist::stat_halfeye() +
  facet_wrap(~ scale) +
  theme_scoringutils() +
  labs(y = "Model", x = "Normalised ranking")

rankings_diff <- rankings |>
  select(model, location, target_end_date, forecast_date, interval_score, scale, ranking) |>
  pivot_wider(names_from = scale, values_from = ranking, id_cols = -interval_score)

p_diff_ranking <- rankings_diff |>
  filter(horizon == 2) |>
  mutate(diff_ranking = natural - log) |>
  mutate(model = factor(model, levels = factor_levels)) |>
  ggplot(aes(y = model, x = diff_ranking)) +
  ggdist::stat_halfeye() +
  theme_scoringutils() +
  labs(y = "", x = "Differences in ranking") +
  theme(axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        axis.line.y = element_blank())

p_rankings + p_diff_ranking + 
  plot_layout(widths = c(2, 1))

ggsave("output/figures/HUB-ranking-diffs.png", width = 9, height = 5)

@@

Check fit of the log scale model

```{r echo=TRUE}
reg_log <- scores |>
  filter(scale == "log") |>
  glm(formula = interval_score ~ 1 + model + location + target_type + horizon, 
      family = gaussian)
```

## Model rankings

Still to do

- restrict to full set of observations
- check how rankings change

```{r}
# find out which models have submitted forecasts for all locations and time points

# Looking at growth rates directly

```{r}
scores_gr |> 
  filter(model == "EuroCOVIDhub-ensemble", 
         horizon == 2) |>
  ggplot(aes(y = interval_score, x = target_type)) + 
  geom_violin(aes(fill = target_type), alpha = 0.2, color = NA) + 
  geom_boxplot(alpha = 0.5) + 
  scale_fill_brewer(palette = "Set1", name = "Forecast target") + 
  facet_wrap(~ scale, scale = "free") + 
  theme_scoringutils() + 
  theme(legend.position = "none") + 
  scale_y_continuous(labels = scale_fn, trans = "log10") + 
  labs(y = "Interval score", x = "Target type")
```

*Scoring the growth rate makes things more comparable*

## Scores for the growth rate across locations

```{r}
scores_gr |> 
  filter(model == "EuroCOVIDhub-ensemble", 
         horizon == 2) |>
  group_by(target_type, location, scale) |>
  summarise(interval_score = mean(interval_score), 
            .groups = "drop_last") |>
  ggplot(aes(y = interval_score, x = reorder(location, -interval_score))) + 
  geom_bar(stat = "identity") + 
  scale_fill_brewer(palette = "Set1", name = "Forecast target") + 
  facet_wrap(~ target_type + scale, scale = "free") + 
  theme_scoringutils() + 
  theme(legend.position = "none") + 
  scale_y_continuous(labels = scale_fn) + 
  labs(y = "Interval score", x = "Target type")
```

## Scores for growth rate over time

restrict to a few locations, e.g. GB, FR, ES (highest average scores there)

UK:

```{r}
scores_gr |> 
  filter(model == "EuroCOVIDhub-ensemble",
         location == "GB",
         horizon == 2) |>
  group_by(target_type, scale) |>
  mutate(multiplicative_score = interval_score / min(interval_score)) |>
  ggplot(aes(y = multiplicative_score, x = forecast_date)) + 
  geom_line() + 
  geom_point() + 
  facet_grid(target_type ~ scale, scale = "free_y") + 
  theme_scoringutils() + 
  labs(x = "Forecast date", y = "WIS relative to smallest observed value")
```

France: Looks like a data revision

```{r}
scores_gr |> 
  filter(model == "EuroCOVIDhub-ensemble",
         location == "FR",
         horizon == 2) |>
  group_by(target_type, scale) |>
  mutate(multiplicative_score = interval_score / min(interval_score)) |>
  ggplot(aes(y = multiplicative_score, x = forecast_date)) + 
  geom_line() + 
  geom_point() + 
  facet_grid(target_type ~ scale, scale = "free_y") + 
  theme_scoringutils() + 
  labs(x = "Forecast date", y = "WIS relative to smallest observed value")
```

Spain:

```{r}
scores_gr |> 
  filter(model == "EuroCOVIDhub-ensemble",
         location == "ES",
         horizon == 2) |>
  group_by(target_type, scale) |>
  mutate(multiplicative_score = interval_score / min(interval_score)) |>
  ggplot(aes(y = multiplicative_score, x = forecast_date)) + 
  geom_line() + 
  geom_point() + 
  facet_grid(target_type ~ scale, scale = "free_y") + 
  theme_scoringutils() + 
  labs(x = "Forecast date", y = "WIS relative to smallest observed value")
```

## Change of average scores for the growth rate for increasing forecast horizons

```{r}
scores_gr |> 
  filter(model == "EuroCOVIDhub-ensemble") |>
  group_by(scale, target_type, horizon) |>
  summarise(interval_score = mean(interval_score), 
            .groups = "drop_last") |>
  mutate(multiplicative_score = interval_score / min(interval_score)) |>
  ggplot(aes(y = multiplicative_score, x = horizon)) + 
  geom_line() + 
  geom_point() + 
  facet_grid(target_type ~ scale) + 
  theme_scoringutils() + 
  labs(x = "Forecast horizon in weeks", y = "Multplicative change in interval score")
```

Check fit of the log scale model

```{r echo=TRUE}
reg_gr <- scores_gr |>
  filter(scale == "natural") |>
  glm(formula = interval_score ~ 1 + model + location + target_type + horizon, 
      family = gaussian)

```{r}
# check distribution
performance::check_distribution(reg_gr_log) |>
  plot()

## Code parking lot

@@

>>>>

ggsave("output/figures/HUB-mean-obs-location.png", width = 9, height = 5.5)

@@

Figure that shows Variance vs. mean of the observations. Makes the point that the
data looks neg. binomial. 
```{r}
# plot with mean vs. variance --------------------------------------------------
hub_data |>
  dplyr::select(location, target_type, target_end_date, true_value) |>
  unique() |>
  group_by(location, target_type) |>
  summarise(mean_value = mean(true_value), 
            sd_value = sd(true_value), 
            var_value = var(true_value)) |>
  ggplot(aes(y = var_value, x = mean_value)) +
  geom_point() + 
  facet_wrap(~ target_type, scales = "free") + 
  scale_x_continuous(trans = "log10", labels = label_fn) +
  scale_y_continuous(trans = "log10", labels = label_fn) +
  # scale_x_continuous(labels = label_fn) +
  # scale_y_continuous(labels = label_fn) +
  labs(y = "Variance observed value", x = "Mean observed value") + 
  geom_function(fun = function(x) {x + x^2}, linetype = "dashed", size = 0.5) + 
  theme_scoringutils() + 
  geom_smooth(alpha = 0.2, size = 0.2)

ggsave("output/figures/HUB-mean-var-obs.png", width = 7, height = 2.5)

@@

@@

```{r}
scores |> 
  filter(model == "EuroCOVIDhub-ensemble") |>
  group_by(scale, target_type, horizon) |>
  summarise(interval_score = mean(interval_score), 
            .groups = "drop_last") |>
  mutate(multiplicative_score = interval_score / min(interval_score)) |>
  ggplot(aes(y = multiplicative_score, x = horizon)) + 
  geom_line() + 
  geom_point() + 
  facet_grid(scale ~ target_type) + 
  theme_scoringutils() + 
  labs(x = "Forecast horizon in weeks", y = "Multplicative change in interval score")

ggsave("output/figures/HUB-scores-over-horizon.png", width = 7, height = 4)

@@

## Comparison of the distribution of model rankings

```{r}

rankings <- scores |>
  select(-c(coverage_deviation, bias, ae_median, dispersion, underprediction, overprediction)) |>
  group_by(location, forecast_date, horizon, target_type, scale) |>
  mutate(ranking = rank(interval_score) / n()) |>
  ungroup()

rankings_diff <- rankings |>
  select(model, location, target_end_date, forecast_date, horizon,
         interval_score, scale, ranking, target_type) |>
  pivot_wider(names_from = scale, values_from = ranking, 
              id_cols = -interval_score)

plot_ranking_diffs <- function(
  rankings, 
  rankings_diff,
  target_type
) {
  type <- target_type
  # maybe replace this by the same ranking for all plots
  factor_levels <- rankings |>
    filter(horizon == 2, scale == "natural", target_type == type) |>
    group_by(model) |>
    summarise(ranking = mean(ranking)) |>
    arrange(-ranking) |>
    pull(model)

  # p_rankings <- rankings |>
  #   filter(horizon == 2) |>
  #   mutate(model = factor(model, levels = factor_levels)) |>
  #   ggplot(aes(y = model, x = ranking)) +
  #   ggdist::stat_halfeye() +
  #   facet_wrap(~ scale) +
  #   theme_scoringutils() +
  #   labs(y = "Model", x = "Normalised ranking")

  ranking_plot <- function(
    hor
  ) {
    p <- rankings_diff |>
      mutate(diff_ranking = natural - log) |>
      mutate(model = factor(model, levels = factor_levels)) |>
      filter(horizon == hor, 
             !is.na(model)) |>
      ggplot(aes(y = model, x = diff_ranking)) +
      geom_vline(linetype = "dashed", xintercept = 0, 
                 size = 0.6, color = "grey40") +
      ggdist::stat_pointinterval() +
      theme_scoringutils() +
      labs(y = "", x = "Differences in ranking")

    if (hor > 1) {
      p <- p +
        theme(axis.text.y = element_blank(), 
              axis.ticks.y = element_blank(), 
              axis.line.y = element_blank())
    }
    return(p)
  }

  ranking_plot(hor = 1) + ranking_plot(2) + ranking_plot(3) + ranking_plot(4) +
    plot_layout(nrow = 1)
}

# should probably have one plot for both cases and deaths since this is rankings
p_diff_cases <- plot_ranking_diffs(rankings, rankings_diff, 
                                   target_type = "Cases")

ggsave(filename = "output/figures/HUB-ranking-diffs.png", 
       plot = p_diff_cases,
       width = 9, height = 5)

@@

--- 
# Code parking lot

@@

Test for a single example forecast to verify that rankings change
```{r}
# we see that rankings change even for a single forecast. So we need to check everything is still correct. 
# take one example
test_data <- hub_data |>
  filter(model %in% c("MUNI-ARIMA", "epiforecasts-EpiNow2"), 
         forecast_date == "2021-10-18", 
         target_type == "Cases", 
         location == "AT")

test_data |>
  mutate(prediction = log(prediction), 
         true_value = log(true_value)) |>
  score(metrics = c("interval_score")) |>
  summarise_scores()
## indeed everything seems to be correct, but rankings still change FOR A SINGLE FORECAST. 
# It seems this is because the trade-off between calibration and sharpness changes? 
# need to check in what way
```

Check fit of the log scale model
```{r echo=TRUE}
reg_log <- scores |>
  filter(scale == "log") |>
  glm(formula = interval_score ~ 1 + model + location + target_type + horizon, 
      family = gaussian)
```

# Growth Rate stuff - Looking at growth rates directly

This uses the Hub ensemble
```{r}
scores_gr |> 
  filter(model == "EuroCOVIDhub-ensemble", 
         horizon == 2) |>
  ggplot(aes(y = interval_score, x = target_type)) + 
  geom_violin(aes(fill = target_type), alpha = 0.2, color = NA) + 
  geom_boxplot(alpha = 0.5) + 
  scale_fill_brewer(palette = "Set1", name = "Forecast target") + 
  facet_wrap(~ scale, scale = "free") + 
  theme_scoringutils() + 
  theme(legend.position = "none") + 
  scale_y_continuous(labels = scale_fn, trans = "log10") + 
  labs(y = "Interval score", x = "Target type")
```
*Scoring the growth rate makes things more comparable*

## Scores for the growth rate across locations
```{r}
scores_gr |> 
  filter(model == "EuroCOVIDhub-ensemble", 
         horizon == 2) |>
  group_by(target_type, location, scale) |>
  summarise(interval_score = mean(interval_score), 
            .groups = "drop_last") |>
  ggplot(aes(y = interval_score, x = reorder(location, -interval_score))) + 
  geom_bar(stat = "identity") + 
  scale_fill_brewer(palette = "Set1", name = "Forecast target") + 
  facet_wrap(~ target_type + scale, scale = "free") + 
  theme_scoringutils() + 
  theme(legend.position = "none") + 
  scale_y_continuous(labels = scale_fn) + 
  labs(y = "Interval score", x = "Target type")
```

## Scores for growth rate over time
restrict to a few locations, e.g. GB, FR, ES (highest average scores there)

UK: 
```{r}
scores_gr |> 
  filter(model == "EuroCOVIDhub-ensemble",
         location == "GB",
         horizon == 2) |>
  group_by(target_type, scale) |>
  mutate(multiplicative_score = interval_score / min(interval_score)) |>
  ggplot(aes(y = multiplicative_score, x = forecast_date)) + 
  geom_line() + 
  geom_point() + 
  facet_grid(target_type ~ scale, scale = "free_y") + 
  theme_scoringutils() + 
  labs(x = "Forecast date", y = "WIS relative to smallest observed value")
```

France: Looks like a data revision
```{r}
scores_gr |> 
  filter(model == "EuroCOVIDhub-ensemble",
         location == "FR",
         horizon == 2) |>
  group_by(target_type, scale) |>
  mutate(multiplicative_score = interval_score / min(interval_score)) |>
  ggplot(aes(y = multiplicative_score, x = forecast_date)) + 
  geom_line() + 
  geom_point() + 
  facet_grid(target_type ~ scale, scale = "free_y") + 
  theme_scoringutils() + 
  labs(x = "Forecast date", y = "WIS relative to smallest observed value")
```

Spain: 
```{r}
scores_gr |> 
  filter(model == "EuroCOVIDhub-ensemble",
         location == "ES",
         horizon == 2) |>
  group_by(target_type, scale) |>
  mutate(multiplicative_score = interval_score / min(interval_score)) |>
  ggplot(aes(y = multiplicative_score, x = forecast_date)) + 
  geom_line() + 
  geom_point() + 
  facet_grid(target_type ~ scale, scale = "free_y") + 
  theme_scoringutils() + 
  labs(x = "Forecast date", y = "WIS relative to smallest observed value")
```

## Change of average scores for the growth rate for increasing forecast horizons
```{r}
scores_gr |> 
  filter(model == "EuroCOVIDhub-ensemble") |>
  group_by(scale, target_type, horizon) |>
  summarise(interval_score = mean(interval_score), 
            .groups = "drop_last") |>
  mutate(multiplicative_score = interval_score / min(interval_score)) |>
  ggplot(aes(y = multiplicative_score, x = horizon)) + 
  geom_line() + 
  geom_point() + 
  facet_grid(target_type ~ scale) + 
  theme_scoringutils() + 
  labs(x = "Forecast horizon in weeks", y = "Multplicative change in interval score")
```

Check fit of the log scale model
```{r echo=TRUE}
reg_gr <- scores_gr |>
  filter(scale == "natural") |>
  glm(formula = interval_score ~ 1 + model + location + target_type + horizon, 
      family = gaussian)

Check distribution
```{r}
# check distribution
performance::check_distribution(reg_gr_log) |>
  plot()

### 2022-07-15 main.tex
update figures, manuscript, add citations

\documentclass{article}
\usepackage[]{graphicx}
\usepackage[]{xcolor}
\usepackage{alltt}
\usepackage[left=2.3cm,right=2.8cm, top = 2.2cm, bottom = 3cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{natbib}
\PassOptionsToPackage{hyphens}{url}
\usepackage{url} 
\usepackage[disable]{todonotes}
\usepackage{multicol}
\usepackage{rotating}
\usepackage{booktabs}
\usepackage[colorlinks=false]{hyperref} 
\setlength{\parskip}{\baselineskip}%
\setlength{\parindent}{0pt}%
\urlstyle{same}
\usepackage{lineno}
\linenumbers

@@

Probabilistic forecasts play an important role in decision-making in epidemiology and public health [Citations], as well as other areas as diverse as for example economics [Citations] or agriculture [Citations]. Epidemiological modelling in particular has received widespread attention during the COVID-19 pandemic and has been an important tool to inform public policy. Evaluating forecasts is important, as the evaluation provides feedback for forecasters and researchers necessary to improve their models, and it helps decision makers with distinguishing good from bad predictions and choosing forecasts that inform future decisions.

Proabbilistic forecasts are usually evaluated using so-called proper scoring rules, which return a numerical score as a function of the forecast and the later observed data. Forecasters, in expectaction, optimise their score by providing a predictive distribution that is equal to the data-generating distribution, and will be penalised if they fail to do so. Two proper scoring rules commonly used in epidemiology and other fields are the Continuous Ranked Probability Score (CRPS) [Gneiting 2007] and the Weighted Interval Score (WIS) [CITATION]. Due to their widespread use in epidemiology we focus on these two in this paper, ignoring other proper scoring rules. Both the WIS and CRPS represent a measure of the absolute distance between the predictive distribution and observation and can be thought of as a generalisation of the absolute error to full predictive distributions (see details in the SI).

Evaluating forecasts based on absolute errors (for simplicity we use the term interchangeably with absolute distance, even though the former technically only applies to point forecasts) may not always be desirable, especially in an epidemiological context. 
% The reason for this is that generally, the way forecasts are evaluated should correspond to the error structure of the model and the type of errors models will usually make.
Epidemiological processes are usually understood to be exponential in nature and therefore are most commonly described and modeled in multiplicative terms. Under the assumption that these models are correctly capturing the underlying inherent transmission dynamics, it would therefore make sense to focus evaluation on multiplicative, rather than absolute errors. Often, if the model is performing badly in multiplicative terms, this means that there is a flaw with its assumptions that needs to be resolved, regardless of performance in absolute terms. Evaluating epidemiological forecasts based on a measure of absolute error (as is common practice) can make it harder to diagnose and quantify model mis-specification. It also may make it more difficult to deal with the potential non-stationarity of epidemiological processes, or to compare performance across targets that are on very different orders of magnitudes (like for example cases and hospitalisations).

In this paper we argue that it may therefore often be helpful to shift the focus of the evaluation on multiplicative, rather than absolute errors. This is approximately equal to scoring the growth rate of a forecast and can be achieved by transforming the forecasts as well as the observations using the logarithm before applying the WIS or CRPS. We focus on the log transformation, as it represents a very convenient way of achieving our goal of evaluating how well a forecast captures the growth dynamic inherent to epidemiological process. However, we note that the same logic we use can also applied to other transformations which could shift the focus of evaluation in different ways. For example, given an appropriate transformation, it could also be possible to evaluate forecasters based on the shape of the trajectory they predicted. It would even be possible to construct composite scores as a weighted sum of scores based on different transformations, allowing forecast consumers to assign explicit weights to different qualities of the forecasts.

In section [REF] we discuss the broader idea of transforming forecasts, and in section [REF] give a detailed theoretical of the log transformation and its interpretation. In section [REF] we present an applied example using forecasts submitted to the European COVID-19 Forecast Hub. The European COVID-19 Forecast Hub is one of several Forecast hubs (together with a Hub in the US [CITATION] and one in Germany and Poland [CITATION]) that systematically collected, aggregated and evaluated forecasts of several COVID-19 targets created by different teams. Forecasts submitted to the COVID-19 Forecast Hubs are probabilistic in nature [Citation e.g. Held et al.], meaning that forecasters provide a full predictive distribution which quantifies their uncertainty. These predictive distributions are reported in the form of a set of 23 quantiles (11 symmetric prediction intervals as well as a median prediction). 
%Currently, the US Flu Forecasting Hub and COVID-19 Scenario Hubs in the US and in Europe use the same format.

@@

The log transformation, among other transformations, is possible because it is a strictly monotonic transformation. A forecast that is closer to the target on the natural scale will still be closer to the target after applying a strictly monotonic transformation like the logarithm. For a single forecast, the ranking between forecasters would be preserved and the scores remain proper, meaning that forecasters still receive the best score in expectation if the predictive distribution equals the data-generating distribution. Differences in the ranking between forecasters only appear when averaging over multiple forecasts, as deviations from the perfect forecast get penalised differently depending on whether forecasts are transformed or not.

\paragraph{First transform, then score, rather than the other way round}
Note that it is important to first apply the transformation and then score the transformed forecasts and observations. Simply taking the log of the WIS or the CRPS computed on the natural scale, i.e. computing $\log S(x, y)$ results in an improper score and is therefore not advised. This is because the logarithm of the WIS / CRPS does not penalise outliers enough and therefore incentivises overconfident predictions. We illustrate this point using simulated data in Figure \ref{fig:log-improper}, where it can easily be seen that overconfident models perform best in terms of the log WIS.

@@

\paragraph{Other transformations}
While we focus on the log transformation in this paper, there are other transformations that may be helpful in an epidemiological context. One could for example divide all forecasts by the population in a location, to obtain forecasts standardised incidences per e.g. 100,000 inhabitants. 
Or one could apply a Box-Cox transformation MISSING. 
Or a square-root transformation MISSING. 
Or one could divide each forecast by the forecast of the previous week (and observations by the observation of the previous week), to transform preditions to week-to-week growth rates. This would be akin to evaluating the shape of the predicted trajectory against the shape of the observed trajectory. Note that this is not well defined in the context of forecasts stored as predictive quantiles, as the growth rate of the $\alpha$-quantile may be different from the $\alpha$-quantile of the growth-rate.

@@

COULD ALSO BE DISCUSSION
Whether or not a log transformation is apprpriate depends on whether one believes that differences in absolute values are meaningful. This may be the case for example when comparing forecasts across locations or time points, rather than different forecasts targets. \citep{Bracher} for example argue that in epidemiological settings it is a desirable property of the CRPS / WIS that it assigns large scores to forecasts where counts are high, as this naturally reflects the situations we should most care about and helps us identify the models that perform best in similar situations. If, on the other hand, we believe that good models should do consistently well and that situations with high incidences do not provide significantly more information about which models perform well or badly, then scoring on the log scale may be more appropriate. For example, it may be reasonable not to think that predictive performance in a country like Germany would have a hundred times more importance than performance in a country like Luxembourg when determining the best model for future decision making. Similarly, we may not necessarily believe that predictive performance during the January 2022 wave of COVID-19 should carry three times as much weight than predictive performance during the January 2021 wave, just because numbers where three times as high. 
% Maybe make a plot with one country and scores for that one country in different waves. We could then argue that within one wave, performance of the peak is meaningful, but across different waves (with different numbers) it is unclear, whether that difference conveys meaningful information.

@@

\paragraph{Introduction to the Forecast Hub} As an empirical example for evaluating forecasts on the natural and on the log scale we use forecasts from the European Forecast Hub \citep{europeancovid-19forecasthubEuropeanCovid19Forecast2021}. Every week the European Forecast Hub collates and aggregates forecasts for different COVID-19 related targets from teams around the world. Forecasts are made one to four weeks ahead into the future and follow a quantile-based format with a set of 22 quantiles plus the median ($0.01, 0.025, 0.05, ..., 0.5, ... 0.95, 0.975, 0.99$). The forecasts for the purpose of this illustrations are two-week-ahead forecasts made between XXX and XXX for reported cases and deaths from COVID-19 in XXX countries.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\textwidth]{output/figures/HUB-mean-var-obs.png}
    \caption{Observed mean against observed variance of observations. The slope of the dashed line is 2, which would represent a relationhip of Variance observed value = square of mean observed value. }
    \label{fig:HUB-variance-mean}
\end{figure}

@@

>>>>

\documentclass{article}
\usepackage[]{graphicx}
\usepackage[]{xcolor}
\usepackage{alltt}
\usepackage[left=2.3cm,right=2.8cm, top = 2.2cm, bottom = 3cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{natbib}
\PassOptionsToPackage{hyphens}{url}
\usepackage{url} 
\usepackage[disable]{todonotes}
\usepackage{multicol}
\usepackage{rotating}
\usepackage{booktabs}
\usepackage[colorlinks=false]{hyperref} 
\setlength{\parskip}{\baselineskip}%
\setlength{\parindent}{0pt}%
\urlstyle{same}
\usepackage{lineno}
\linenumbers
\bibliographystyle{apalike}

@@

Probabilistic forecasts play an important role in decision-making in epidemiology and public health \citep{reichCollaborativeMultiyearMultimodel2019, funkShorttermForecastsInform2020, cramerEvaluationIndividualEnsemble2021, bracherShorttermForecastingCOVID192021, europeancovid-19forecasthubEuropeanCovid19Forecast2021, sherrattPredictivePerformanceMultimodel2022}, as well as other areas as diverse as for example economics \citep{timmermannForecastingMethodsFinance2018, elliottForecastingEconomicsFinance2016} or meteorology \citep{gneitingWeatherForecastingEnsemble2005, kukkonenReviewOperationalRegionalscale2012}. Epidemiological modelling in particular has received widespread attention during the COVID-19 pandemic and has been an important tool to inform public policy. Evaluating forecasts is important, as the evaluation provides feedback for forecasters and researchers necessary to improve their models, and it helps decision makers distinguish good from bad predictions and choosing forecasts that inform future decisions.

Proabbilistic forecasts are usually evaluated using so-called proper scoring rules, which return a numerical score as a function of the forecast and the later observed data. Forecasters, in expectaction, optimise their score by providing a predictive distribution that is equal to the data-generating distribution, and will be penalised if they fail to do so. Two proper scoring rules commonly used in epidemiology and other fields are the Continuous Ranked Probability Score (CRPS) \citep{gneitingStrictlyProperScoring2007} and the Weighted Interval Score (WIS) \citep{bracherEvaluatingEpidemicForecasts2021}. Due to their widespread use in epidemiology we focus on these two in this paper, ignoring other proper scoring rules. Both the WIS and CRPS represent a measure of the absolute distance between the predictive distribution and observation and can be thought of as a generalisation of the absolute error to full predictive distributions (see details in the SI).

Evaluating forecasts based on absolute errors (for simplicity we use the term interchangeably with absolute distance, even though the former technically only applies to point forecasts) may not always be desirable, especially in an epidemiological context. 
% The reason for this is that generally, the way for ecasts are evaluated should correspond to the error structure of the model and the type of errors models will usually make.
Epidemiological processes are usually understood to be exponential in nature and therefore are most commonly described and modeled in multiplicative terms. Under the assumption that these models are correctly capturing the underlying inherent transmission dynamics, it would therefore make sense to focus evaluation on multiplicative, rather than absolute errors. Often, if the model is performing badly in multiplicative terms, this means that there is a flaw with its assumptions that needs to be resolved, regardless of performance in absolute terms. Evaluating epidemiological forecasts based on a measure of absolute error (as is common practice) can make it harder to diagnose and quantify model mis-specification. It also may make it more difficult to deal with the potential non-stationarity of epidemiological processes, or to compare performance across targets that are on very different orders of magnitudes (like for example cases and hospitalisations).

In this paper we argue that it may therefore be helpful to shift the focus of the evaluation on multiplicative, rather than absolute errors. This is approximately equal to scoring the growth rate of a forecast and can be achieved by transforming the forecasts as well as the observations using the logarithm before applying the WIS or CRPS. We focus on the log transformation, as it represents a very convenient way of achieving our goal of evaluating how well a forecast captures the growth dynamic inherent to epidemiological process. However, we note that the same logic we use can also applied to other transformations which could shift the focus of evaluation in different ways. For example, given an appropriate transformation, it could also be possible to evaluate forecasters based on the shape of the trajectory they predicted. It would even be possible to construct composite scores as a weighted sum of scores based on different transformations, allowing forecast consumers to assign explicit weights to different qualities of the forecasts.

In section [REF] we discuss the broader idea of transforming forecasts, and in section [REF] give a detailed theoretical of the log transformation and its interpretation. In section [REF] we present an applied example using forecasts submitted to the European COVID-19 Forecast Hub \citep{europeancovid-19forecasthubEuropeanCovid19Forecast2021, sherrattPredictivePerformanceMultimodel2022}. The European COVID-19 Forecast Hub is one of several Forecast hubs (together with a Hub in the US \citep{cramerEvaluationIndividualEnsemble2021} and one in Germany and Poland \citep{bracherShorttermForecastingCOVID192021} that systematically collected, aggregated and evaluated forecasts of several COVID-19 targets created by different teams. Forecasts submitted to the COVID-19 Forecast Hubs are probabilistic in nature [Citation e.g. Held et al.], meaning that forecasters provide a full predictive distribution which quantifies their uncertainty. These predictive distributions are reported in the form of a set of 23 quantiles (11 symmetric prediction intervals as well as a median prediction). 
%Currently, the US Flu Forecasting Hub and COVID-19 Scenario Hubs in the US and in Europe use the same format.

@@

Applying the log transformation, among other transformations, is permissible because it is a strictly monotonic transformation. While rankings between different models may indeed change, even for a single forecast, the relevant condition for a scoring rule to be strictly proper is still satisfied: In expectation a forecaster will receive the best score if she reports a predictive distribution that is equal to the data-generating distribution, even after transforming both the forecasts and the observations (representing draws from the data-generating distribution).

It is important to first apply the transformation and then score the transformed forecasts and observations. Simply taking the log of the WIS or the CRPS computed on the natural scale, i.e. computing $\log S(x, y)$ results in an improper score and is therefore not advised. This is because the logarithm of the WIS / CRPS does not penalise outliers enough and therefore incentivises overconfident predictions. We illustrate this point using simulated data in Figure \ref{fig:log-improper}, where it can easily be seen that overconfident models perform best in terms of the log WIS.

@@

\paragraph{Other transformations - maybe move to Discussion}
While we focus on the log transformation in this paper, there are other transformations that may be helpful in an epidemiological context. One could for example divide all forecasts by the population in a location, to obtain forecasts standardised incidences per e.g. 100,000 inhabitants. 
Or one could apply a Box-Cox transformation MISSING. 
Or a square-root transformation MISSING. 
Or one could divide each forecast by the forecast of the previous week (and observations by the observation of the previous week), to transform preditions to week-to-week growth rates. This would be akin to evaluating the shape of the predicted trajectory against the shape of the observed trajectory. Note that this is not well defined in the context of forecasts stored as predictive quantiles, as the growth rate of the $\alpha$-quantile may be different from the $\alpha$-quantile of the growth-rate.

@@

COULD ALSO BE DISCUSSION
Whether or not a log transformation is apprpriate depends on whether one believes that differences in absolute values are meaningful. This may be the case for example when comparing forecasts across locations or time points, rather than different forecasts targets. \cite{bracherEvaluatingEpidemicForecasts2021} for example argue that in epidemiological settings it is a desirable property of the CRPS / WIS that it assigns large scores to forecasts where counts are high, as this naturally reflects the situations we should most care about and helps us identify the models that perform best in similar situations. If, on the other hand, we believe that good models should do consistently well and that situations with high incidences do not provide significantly more information about which models perform well or badly, then scoring on the log scale may be more appropriate. For example, it may be reasonable not to think that predictive performance in a country like Germany would have a hundred times more importance than performance in a country like Luxembourg when determining the best model for future decision making. Similarly, we may not necessarily believe that predictive performance during the January 2022 wave of COVID-19 should carry three times as much weight than predictive performance during the January 2021 wave, just because numbers where three times as high. 
% Maybe make a plot with one country and scores for that one country in different waves. We could then argue that within one wave, performance of the peak is meaningful, but across different waves (with different numbers) it is unclear, whether that difference conveys meaningful information.

@@

\paragraph{Introduction to the Forecast Hub} As an empirical example for evaluating forecasts on the natural and on the log scale we use forecasts from the European Forecast Hub \citep{europeancovid-19forecasthubEuropeanCovid19Forecast2021, sherrattPredictivePerformanceMultimodel2022}. Every week the European Forecast Hub collates and aggregates forecasts for different COVID-19 related targets from teams around the world. Forecasts are made one to four weeks ahead into the future and follow a quantile-based format with a set of 22 quantiles plus the median ($0.01, 0.025, 0.05, ..., 0.5, ... 0.95, 0.975, 0.99$). The forecasts for the purpose of this illustrations are two-week-ahead forecasts made between XXX and XXX for reported cases and deaths from COVID-19 in XXX countries.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\textwidth]{output/figures/HUB-mean-var-obs.png}
    \caption{Observed mean against observed variance of observations. The dashed line marks what would be expecetd from a negative binomially distributed variable with variance of the observed value equal to the mean + the square of mean observed value. }
    \label{fig:HUB-variance-mean}
\end{figure}

@@

\bibliography{log-or-not.bib}
